Do moral communities have a spatial dimension? A spatial exploratory analysis of places of worship and violent crime in the city of Recife, Brazil

### 2020-05-18 Moral-Communities-and-Crime/Moral_Communities_and_Crime.Rmd
Tidied up folders before revisions for version 2

authors: 
- name: Aye B. Cee
  address: A Department, University of XXX
  email: abc@example.edu

- name: Dee E. Eff
  address: A Department, University of XXX
  email: def@example.edu

- name: Gee H. Eye
  address: A Department, University of XXX
  email: ghi@example.edu

- name: Jay K. Elle
  address: Some School, University of WWW
  email: jkl@school.edu

>>>>

authors: 
- name: Author One
  address: A Department, University of XXX
  email: abc@example.edu

- name: Author Two
  address: A Department, University of XXX
  email: def@example.edu

- name: Author Three
  address: A Department, University of XXX
  email: ghi@example.edu

- name: Author Four
  address: Some School, University of WWW
  email: jkl@school.edu

### 2020-05-18 Moral-Communities-and-Crime/Moral_Communities_and_Crime_Title_Page.Rmd
Tidied up folders before revisions for version 2

---
title: Do moral communities have a spatial dimension? A spatial exploratory analysis of places of worship and violent crime in the city of Recife, Brazil
subtitle: 
titlerunning: Moral communities and crime
authorrunning: 
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

>>>>

---
title: Do moral communities have a spatial dimension? A spatial exploratory analysis of places of worship and violent crime in the city of Recife, Brazil
subtitle: 
titlerunning: Moral communities and crime
authorrunning: 
thanks: | 
    **Funding:** Edivaldo Constantino das Neves Júnior received support from the Government of Canada, through the program Emerging Leaders in the Americas. **Conflicts of Interest:** The authors declare that they have no conflict of interest.
